Mitigating Low Audio Quality by Domain Transfer for Better ASR

### 2020-04-12 2020-tsd-brno-denoise/denoise.tex
tsd 2020 denoise: remove years from inline citations

For speech recognition, the problem of noise, reverberation and other defects
has been a pain point and also a point of research. To mention some, Gillespie
and Atlas (2002)\cite{gillespie2002diversity} deal with reverberation for
GMM-based ASR, Yoshioka et al. (2012)\cite{reverbmagazine} summarize various
dereverberation techniques, Ko et al. (2017)\cite{reverbaugment} attempt to
simlulate reverberation in training data digitally. Seltzer, Yu and Wang
(2013)\cite{dnnnoiserobust} deal with noise in DNN-based ASR.

@@

The revolutionary article of Zhu et al. (2017)\cite{cyclegan} presenting
cycle-consistent generative adversarial networks gave mankind a mighty tool and
a hilarious toy that was used for de-hazing
photographs\cite{Engin_2018_CVPR_Workshops}, giving people other's facial
expressions\cite{jin2017faceoff}, in biomedicine\cite{yang2018biogan} and also
in speech processing: Kaneko and Tameoka (2017)\cite{kaneko2017parallel} present
speech domain transfer and Hosseini-Asl et al.
(2018)\cite{hosseini2018malevoicegan} do the same for the purpose of speech
recognition.

@@

In order to perform clustering on any dataset, a metric on the data is needed.
I have used that proposed by Mandel \& Ellis (2005)\cite{mandel2005song}, which
is based on mel-frequency cepstra. A distance matrix has been created using the
tool musly\cite{schnitzer2011using} and the clusters on top of that using
hierarchical clustering\cite{johnson1967hierarchical}.

@@

I have used the voice transfer method as proposed by Kaneko \& Kameoka
(2017)\cite{kaneko2017parallel} and implemented by
Mao\footnote{github.com/leimao/Voice\_Converter\_CycleGAN}. I have trained
transfer 1) between the clean and the overdriven cluster and 2) between the
clean and the low-speed cluster.

>>>>

For speech recognition, the problem of noise, reverberation and other defects
has been a pain point and also a point of research. To mention some, Gillespie
and Atlas\cite{gillespie2002diversity} deal with reverberation for
GMM-based ASR, Yoshioka et al.\cite{reverbmagazine} summarize various
dereverberation techniques, Ko et al.\cite{reverbaugment} attempt to
simlulate reverberation in training data digitally. Seltzer, Yu and
Wang\cite{dnnnoiserobust} deal with noise in DNN-based ASR.

@@

The revolutionary article of Zhu et al.\cite{cyclegan} presenting
cycle-consistent generative adversarial networks gave mankind a mighty tool and
a hilarious toy that was used for de-hazing
photographs\cite{Engin_2018_CVPR_Workshops}, giving people other's facial
expressions\cite{jin2017faceoff}, in biomedicine\cite{yang2018biogan} and also
in speech processing: Kaneko and Tameoka\cite{kaneko2017parallel} present
speech domain transfer and Hosseini-Asl et al.\cite{hosseini2018malevoicegan} do
the same for the purpose of speech recognition.

@@

In order to perform clustering on any dataset, a metric on the data is needed.
I have used that proposed by Mandel \& Ellis\cite{mandel2005song}, which
is based on mel-frequency cepstra. A distance matrix has been created using the
tool musly\cite{schnitzer2011using} and the clusters on top of that using
hierarchical clustering\cite{johnson1967hierarchical}.

@@

I have used the voice transfer method as proposed by Kaneko \&
Kameoka\cite{kaneko2017parallel} and implemented by
Mao\footnote{github.com/leimao/Voice\_Converter\_CycleGAN}. I have trained
transfer 1) between the clean and the overdriven cluster and 2) between the
clean and the low-speed cluster.
